Structural controllability of ecological networks

### 2018-06-26 paper/cover-letter.tex
spell check is Fernando's least favorite part of writing, but Daniel loves it

Adopting a primarily conceptual focus has allowed us to be clearer about the justification, methodology and potential insights of our approach. 
However, improving clarity while successfully tying the conceptual motivation with our findings required more than some changes to some paragraphs or sections of the manuscript. 
Therefore, we have rewritten almost entirely the manuscript and the supplementary materials. 
We maintain the methodology and findings, but there has been a major change in the way we justify the study, introduce novel concepts to the ecological domain, emphasize resulys, and present our conclusions.

>>>>

Adopting a primarily conceptual focus has allowed us to be clearer about the justification, methodology and potential insights of our approach. 
However, improving clarity while successfully tying the conceptual motivation with our findings required more than some changes to some paragraphs or sections of the manuscript. 
Therefore, we have rewritten almost entirely the manuscript and the supplementary materials. 
We maintain the methodology and findings, but there has been a major change in the way we justify the study, introduce novel concepts to the ecological domain, emphasize results, and present our conclusions.
